A multi-dimensional extension of the Lightweight Temporary Compression method

### 2018-10-12 paper.tex
write result first version

\section{Implementation}
Our code is available at ... (make a clean release!)
/todo{below content is useful? }
\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively. But we did some changes in our method. Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$. cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
After that updating tolerance range by adding designed error margin which after mapping
$\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.

@@

\subsection{Multidimensional LTC with Euclidean distance}
In Euclidean distance version, we also map the coming data into same time-stamp $t_1$ the timestamp after base point. The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension. In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them. For instance, in 3D-t, assume we have a the base point $Z = D_0$ and the tolerance range $R_1$ which is a ball as the intersection S. we need a list L to record mapped balls from $D_1$ to coming data. For each comming data $D_i, i>1$ mapping this data into $t_1$, and add it into list. Then the work is check out if all balls intersect, and form a public intersection. The method is based on plane sweep and binary search. At first, select one parameter, such as x-axis, finding a bounding range of all balls $B_i$ in x-axis. suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and $Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$. If there is overlap among balls, then the axis of the points inside intersection must located between Min_bound_x and Max_bound_x. Using binary search to select mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding with the plane x = mid_x. If the get bounding range in y-axis where $Max_bound_y > Min_bound_y$ and using binary search again to find mid_y, It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y, parallels z-axis, could pass through all balls. Finally, in z-axis, compute bounding range, and If $Max_bound_z > Min_bound_z$, there must be one or more points inside all balls. The problem be solved. If the loop of binary search in x-axis overs, then there is no public intersection among balls, and need to transmit and update base point. In this method we need O(n*logn*logn) time complexity for binary search in x-axis and y-axis and traversal all balls in z-axis, also O(n) space complexity is needed for maintaining list. According this method, it could be extended into N-dimensional data. The main idea is to search, dimension by dimension, from a room or plane or line and get intersection point finally.

/todo{below content is useful? }
In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
\begin{itemize}
\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk. After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data. Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis. So In 3-dimension whether \textit{n} balls intersect need to be check.
\end{itemize}

@@

\subsection{Experiment 1: energy reduction on the Neblina}

@@

@@

>>>>

\section{Implementation}
Our code is available at ... (make a clean release!)
\todo{below content is useful? }
\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively. But we did some changes in our method. Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$. cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
After that updating tolerance range by adding designed error margin which after mapping
$\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.

@@

\subsection{Multidimensional LTC with Euclidean distance}
In Euclidean distance version, we also map the coming data into same time-stamp $t_{1}$ the timestamp after base point. The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension. In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them. For instance, in 3D-t, assume we have a the base point $Z = D_{0}$ and the tolerance range $R_{1}$ which is a ball as the intersection S. we need a list L to record mapped balls from $D_{1}$ to coming data. For each comming data $D_i, i>{1}$ mapping this data into $t_{1}$, and add it into list. Then the work is check out if all balls intersect, and form a public intersection. The method is based on plane sweep and binary search. At first, select one parameter, such as x-axis, finding a bounding range of all balls $B_i$ in x-axis. suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and $Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$. If there is overlap among balls, then the axis of the points inside intersection must located between Min_bound_x and Max_bound_x. Using binary search to select mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding with the plane x = mid_x. If the get bounding range in y-axis where $Max_bound_y > Min_bound_y$ and using binary search again to find mid_y, It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y, parallels z-axis, could pass through all balls. Finally, in z-axis, compute bounding range, and If $Max_bound_z > Min_bound_z$, there must be one or more points inside all balls. The problem be solved. If the loop of binary search in x-axis overs, then there is no public intersection among balls, and need to transmit and update base point. In this method we need O(n*logn*logn) time complexity for binary search in x-axis and y-axis and traversal all balls in z-axis, also O(n) space complexity is needed for maintaining list. According this method, it could be extended into N-dimensional data. The main idea is to search, dimension by dimension, from a room or plane or line and get intersection point finally.

\todo{below content is useful? }
In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
\begin{itemize}
\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk. After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data. Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis. So In 3-dimension whether \textit{n} balls intersect need to be check.
\end{itemize}

@@

\subsection{Experiment 2: energy reduction on the Neblina}

@@

The experiment in Neblina, we weared Neblina on right wrist and
collected walking data and running data. 4000 data set was collected
from Neblina in 200Hz sampling rate. Since arm swing appearance
repeated, we just take 1000 data from it, and make data as cycle of
these 1000 data. Because 1000 data is produced in 5 seconds with 200Hz
sampling rate, we measured average energy usage in 5 seconds.

At first, we measured base energy usage in Neblina. The energy usage
without transmision is 2.515 mAh. It is 3.472mAh with transmision but
no compression method. From table 3 and table 4, The MaxError don't exceed EPSILON
and EPSILON*sqrt(Dimension) with LTC-Euclidean and LTC-Manhatan respectively.
And the average electric current increase with compression radio decreasing.
Energy usage by using both compression method are smaller than transmit
without compression. From the result, the activities which has low frequency
would gain larger compression radio.

The purpose of the compression method is compressing the number of
data needed to transmited, in order to extend Neblna's life cycle
by decreasing energy consumption. From table 3, for not vigorous exercise
such walking, with EPSILON equals 100, the life cycle could be extend
3(10\%)and 9(31\%) hours with LTC-Euclidean and LTC-Manhattan respectively.
And vigorous exercise, with same condition, it extends 5.7(19.7\%)
and 4.8(16.7\%) hours. So LTC-Euclidean and LTC-Manhattan are useful
to save devices Energy. At same time, The fidelity is guaranteed.

@@

\begin{table}[]
\begin{tabular}{lllllll}
DataSet           & \multicolumn{6}{l}{walking}                                   \\
Distance          & \multicolumn{3}{l}{Manhattan} & \multicolumn{3}{l}{Euclidean} \\
Epsilon           & 100       & 20      & 10      & 100       & 20      & 10      \\
Max Error         & 158.793   & 31.828  & 16.763  & 153.141   & 31.763  & 15.898  \\
Compression Radio & 88.9\%    & 66.4\%  & 45.5\%  & 68.6\%    & 25.5\%  & 9.5\%   \\
Energy Usage      & 2.642     & 2.787   & 3.020   & 2.879     & 3.221   & 3.383
\end{tabular}
\end{table}

\begin{table}[]
\begin{tabular}{lllllll}
DataSet           & \multicolumn{6}{l}{running}                                   \\
Distance          & \multicolumn{3}{l}{Manhattan} & \multicolumn{3}{l}{Euclidean} \\
Epsilon           & 100      & 20       & 10      & 100      & 20       & 10      \\
Max Error         & 99.995   & 19.984   & 9.979   & 99.995   & 19.989   & 9.959   \\
Compression Radio & 87.6\%   & 63.3\%   & 37.2\%  & 64.4\%   & 19.8\%   & 5.7\%   \\
Energy Usage      & 3.098    & 3.020    & 3.134   & 2.952    & 3.320    & 3.393
\end{tabular}
\end{table}
